Detection of defects in additive manufacturing from a single x-ray projection using the empirical null filter

### 2019-08-09 reports/paper1/paper.tex
corrected paper

A disadvantage of XCT is that it involves the acquisition and reconstruction of thousands of projections of the sample. XCT is not an instantaneous process so progress bars are usually featured XCT marketing such as \emph{Nikon}'s inline quality control \citep{nikon2015inline}. Projection acquisition can take between 15 minutes to a number of hours \citep{warnett2016towards} but more projections would improve the accuracy of the reconstruction \citep{kruth2011computed}.

@@

In the experiment with the test sample, the angle was chosen to distinguish the designed voids. For general AM products, finding a suitable singular projection angle can be difficult. This problem can be tackled by conducting defect detection on a small number of different angular projections independently to pick up defects hidden behind another.

>>>>

A disadvantage of XCT is that it involves the acquisition and reconstruction of thousands of projections of the sample. XCT is not an instantaneous process so progress bars are usually featured in XCT marketing such as \emph{Nikon}'s inline quality control \citep{nikon2015inline}. Projection acquisition can take between 15 minutes to a number of hours \citep{warnett2016towards} but more projections would improve the accuracy of the reconstruction \citep{kruth2011computed}.

@@

In the experiment, the angle was chosen to distinguish the designed voids. For general AM products, finding a suitable singular projection angle can be difficult. This problem can be tackled by conducting defect detection on a small number of different angular projections independently to pick up defects hidden behind another.
